### 2014-03-07 docs/related-work.tex
SkypeMorph is called Code Talker Tunnel now.
GoAgent paragraph.

Traffic using covert channels may exhibit distinguishable characteristics. As
noted by Winter et al.~\cite{foci12-winter}, Tor traffic is currently
distinguishable from what is regarded as harmless traffic. Therefore, another
school of research focuses on obfuscation techniques for hiding protocol
patterns. One technique is to look unlike anything forbidden by the censor; that
is, fail to match a blacklist. Another is to resemble a protocol that is
explicitly allowed; that is, match a whitelist. Falling into the first category
are ``look-like-nothing'' transports whose payloads are indistinguishable from a
uniformly random byte stream. A examples of such a transport is
obfsproxy~\cite{obfsproxy}, long the go-to obfuscated transport used by Tor.
ScrambleSuit~\cite{scramblesuit} is like obfsproxy in the content of its
payloads, but takes additional steps to obscure its signature of packet lengths
and timing, and is designed to resist active scanning for proxies (the proxy
server says nothing until the client proves knowledge of a shared secret).
Another path to obfsucation is the steganographic approach: look like something
the censor doesn't block. StegoTorus~\cite{stegotorus} and SkypeMorph~\cite{skypemorph} camouflage Tor
traffic and attempt to mimic HTTP or Skype traffic.\\

@@

GoAgent\\

>>>>

Traffic using covert channels may exhibit distinguishable characteristics. As
noted by Winter et al.~\cite{foci12-winter}, Tor traffic is currently
distinguishable from what is regarded as harmless traffic. Therefore, another
school of research focuses on obfuscation techniques for hiding protocol
patterns. One technique is to look unlike anything forbidden by the censor; that
is, fail to match a blacklist. Another is to resemble a protocol that is
explicitly allowed; that is, match a whitelist. Falling into the first category
are ``look-like-nothing'' transports whose payloads are indistinguishable from a
uniformly random byte stream. A examples of such a transport is
obfsproxy~\cite{obfsproxy}, long the go-to obfuscated transport used by Tor.
ScrambleSuit~\cite{scramblesuit} is like obfsproxy in the content of its
payloads, but takes additional steps to obscure its signature of packet lengths
and timing, and is designed to resist active scanning for proxies (the proxy
server says nothing until the client proves knowledge of a shared secret).
Another path to obfsucation is the steganographic approach: look like something
the censor doesn't block. StegoTorus~\cite{stegotorus} and Code Talker Tunnel (formerly called SkypeMorph)~\cite{skypemorph} camouflage Tor
traffic and attempt to mimic HTTP or Skype traffic.\\

@@

GoAgent~\cite{goagent} is a direct inspiration for our work in its use of App Engine
and Host header--based domain fronting.
GoAgent requires users to upload a personal copy of the server code to App Engine,
and App Engine itself makes HTTP requests, not some proxy farther out.
According to a May 2013 survey~\cite{collateral-freedom},
GoAgent was then the circumvention tool most used in China,
with 35\% of survey respondants having used it in the previous month.
This figure is higher than that of paid~(29\%) and free VPNs~(18\%),
and far above that of other special-purpose tools like Tor~(2.9\%)
and Psiphon~(2.5\%).
\\
